Solving smooth system of algebraic equations

### 2021-05-28 article/conventions.tex
work on article
article

We use on $\PNR$ the measure induced by
the chord metric of the unit sphere:
$$d(\overline{x},\overline{y}) = \min\left(
\left\|{\frac{x}{\|x\|}} - {\frac{y}{\|y\|}}\right\|, \left\|{\frac{x}{\|x\|}} + {\frac{y}{\|y\|}}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$

If $x ∈ \PNR$ (resp. $ℝ^{n+1}$), $\ball{x}{r}$ denotes the closed ball of center $x$
and radius $r$.

@@

For $A ⊂ ℝ^{n+1}$, $\hull{A}$ denotes the convex hull of $A$ and $\cone{A}$ its
convex cone.

>>>>

We use on $\PNR$ the measure and topology induced by
the chord metric of the unit sphere:
$$d(\overline{x},\overline{y}) = \min\left(
\left\|{\frac{x}{\|x\|}} - {\frac{y}{\|y\|}}\right\|, \left\|{\frac{x}{\|x\|}} + {\frac{y}{\|y\|}}\right\|\right) (∀\overline{x},\overline{y} ∈ \PNR).$$

If $x ∈ \PNR$ (resp. $ℝ^{n+1}$), $\ball{x}{r}$ denotes the open ball of center $x$
and radius $r$ and $\cball{x}{r}$ denotes its closure.

@@

For $A ⊂ ℝ^{n+1}$, $\hull{A}$ denotes the convex hull of $A$ and $\cone{A}$ its
convex cone:
$$\cone{A} = \{ ∑_{i=0}ⁿ λᵢ xᵢ, x₀,\dots,xₙ ∈ A, λ₀,\dots,λₙ∈ℝ^⋆₊\}$$
$$\hull{A} = \{ ∑_{i=0}ⁿ λᵢ xᵢ, x₀,\dots,xₙ ∈ A, λ₀,\dots,λₙ∈ℝ^⋆₊,
∑_{i=1}ⁿ λᵢ=1 \}$$
